\documentclass[11pt]{article}
\usepackage{enumerate}
\usepackage[margin=1in]{geometry}

% header stuff
\newcommand{\myheader}[4]{%
	\vspace*{-0.5in}
	\noindent
	{#1} \hfill {#3}\\
	{#2} \hfill {#4}\\
	\rule[8pt]{\textwidth}{1pt}
}

\newcommand{\mytitle}[2]{%
	\begin{center}
		{\large {\bf #1}}\\
		\bigskip
		#2\\ % name goes here
		\medskip
	\end{center}
}

\begin{document}

\myheader{Ma House}{}{Summer 2015}{}
\mytitle{Hot Questions}{Andrew \& Jason}

\begin{enumerate}
	\item Imagine that everyone around you had a bubble floating above their head which displayed one piece of information about
		them to you. What would you like to know? (i.e. What would you like to know about everybody for free?)
		\begin{enumerate}[(a)]
			\item Now, you are the one with the bubble above your head that everyone else can see. What would you want people to know
				about you?
			\item What if it was just your partner that had a bubble above their head, what would you want to know? (and vice versa).
		\end{enumerate}

	\item What do you think (\emph{insert name}) as wrong about you?

	\item How many (significant to you) things have you never told anyone?
		\begin{enumerate}[(a)]
			\item Compile a list of people who, if they asked you for these secrets, you would tell them to.
			\item Who do you think, thinks that they are on your list?
			\item Whose list do you think you're on?
		\end{enumerate}

	\item How many people do you think should be on someone's list? 
	\item What topics make you feel vulnerable?
	\item Have you ever asked something of someone (or a question) that you knew would put strain on the relationship?
	\item Who would you drive across town at 7pm for? At 3am? To Nanaimo? Fly to them?
	\item Suppose you had a love potion that made the person you sprayed it with fall deeply and happily in love with you.
		Would you use this love potion? Is it immoral to use it?
		\begin{enumerate}
			\item Suppose you asked them first?
			\item Suppose you were a master seducer and you had the ability to make people fall in love with you, is it 
				immoral to use this power?

			\item The one with the investor and the couple...
		\end{enumerate}

	\item What's a behaviour that you wanted to change and then did?
	\item What have you worked the hardest for?
	\item What's the youngest you could believe someone was really in love?
	\item Is there a difference between how you love your friends and how you love your partner? Or, are they similar but 
		with your partner you have an added component of sex/physical intimacy.
	\item Which friend of yours do you think you could help the most?
	\item Imagine we had made contact with Aliens and you've been asked to leave earth in a spaceship on a journey to the alien 
		world. You are allowed to bring up to 25 people and can outfit your spaceship as luxuriously as you like (within reason).
		It's going to take 30 years to get there. Would you go? Adjust the number of years and people they can take depending on 
		their answers.
	\item Does everyone have a duty to make the world a better place? How do you do that?
	\item What confuses you about people?
	\item What's something about yourself that you'd like to change?
	\item When was the last time you cried?
	\item Who would you feel comfortable crying in front of?
	\item What do you think most people have wrong about you?
	\item Imagine your doctor told you that you were getting dementia and that he could preserve one memory for certain.
		Which memory would you keep?



	





\end{enumerate}

\end{document}
